\documentclass[10pt]{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{palatino}
\usepackage{titlesec}

\titlespacing{\subsubsection}{0pt}{0.1\baselineskip}{0.2\baselineskip}
\pagenumbering{gobble}

\begin{document}

\begin{center}
	\LARGE{\textbf{Christopher Carter}} \\
	\medskip
	\normalsize{
		(802) 458-7731 \textbar\space carterce1997@gmail.com \textbar\space linkedin.com/in/chris-e-carter/
	}
\end{center}

\hrule

\subsection*{Professional Summary}
Trained mathematician with a deep knowledge of mathematics, data, and computing acquired over 5 years of experience in numerous fields, including data science, data engineering, software engineering, web technologies, cloud computing, and Linux systems. Dedicated to excellence and reviving American innovation and integrity.

\subsection*{Experience}

\subsubsection*{Cloud Data Engineer, Mindex (2023-Present)}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
\item Delivered a cloud data analytics application based on AWS Glue, Quicksight, Lambda, API Gateway, and other serverless resources to augment Mindex’s flagship product with novel data analytics capabilities and third party data access.
\item Implemented a continuous delivery pipeline using AWS CDK and CodePipeline to scale the application to over 400 school districts in New York State, allowing changes to be delivered within minutes if necessary.
\item Implemented architectural optimizations resulting in over 30\% cost savings on ETL processes. Maintained and enhanced the application with no significant downtime or production issues while still rapidly delivering features approximately every two weeks.
\end{itemize}

\subsubsection*{Freelance Developer, Camp Li-Lo-Li (2023-Present)}

\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\item Currently working with a local Christian camp to develop a web app for counselors to manage camper achievements and badges (such as fire starting, first aid, etc.). Worked with key stakeholders in camp governance to gather requirements and understand pain points of the legacy system.
	\item Implemented all backend data modeling and business logic in Django, integrated the app with the existing CampWise camp management system, and designed a reactive frontend UI using Bulma and vanilla JavaScript.
\end{itemize}


\subsubsection*{Data Engineer, Raymour and Flanigan (2021-2023)}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
\item Responsible for the deployment, maintenance, and improvement of a Snowflake data warehouse containing enterprise critical dimension tables and fact tables, views, cron tasks, procedures, and other database objects. 
\item Delivered critical third-party customer data to marketing and leadership, resulting in a 3.7x level of enrichment, the novel realization of RFM metrics at the individual and household level, and a 10\% increase in customer mailing address accuracy.
\item Trained team members in Matillion ETL, facilitating an overall fourfold increase in BI team ETL productivity.
\end{itemize}

\subsubsection*{Data Scientist, L3Harris Technologies (2019-2021)}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
\item Developed a nowcasting system to detect possible disruptions to global supply chain partners due to weather, earthquakes, wildfires, and other phenomena using geospatial data analysis, providing an early warning to the supply chain team of the growing extent of the COVID-19 pandemic. 
\item Designed and implemented a regression model to regress cost savings from volume pricing, resulting in novel visibility into volume pricing opportunities for electronic components. 
\item Developed an end-to-end view of future inventory movement at the individual part level, giving production planners a real-time view into when the expected level of inventory for a part would become 0.
\end{itemize}

\subsection*{Skills}
\begin{itemize}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}
	\item \textbf{Software Engineering}: Cloud Computing, Backend Web Engineering, Linux, AWS, Django, Flask, Hugo
	\item \textbf{Data Engineering}: Dimensional Modeling, ETL/ELT, AWS Glue, Snowflake, SQL, Relational Databases
	\item \textbf{Programming}: Python, R, Rust, C/C++, HTML/CSS/JS, Vim, Git
	\item \textbf{Data Analysis}: Bayesian Statistics, Mathematical Modeling, Machine Learning, Data Mining and Visualization
\end{itemize}

\subsection*{Education}
\textbf{Clarkson University} \\
Bachelor of Science in Mathematics, 2019 (GPA: 3.87/4.00)\\
Prominent Coursework: Bayesian Statistics, Mathematical Modeling, Algorithms and Data Structures


\end{document}
